Structured Versus Decorated Cospans

### 2020-12-23 cospans.tex
changed 3 things related to eq. (10); see comments marked "jb"

This can always be achieved by replacing $F$ by an equivalent pseudofunctor that strictly preserves identity morphisms, but we do this merely to reduce the size of diagrams to come; the reader can reinsert the morphism $F(!_0)$ where needed. %%% see if you like this!  I'd like to add a ref that says any 2-functors is equivalent to a normalized one. - jb
The associator is formed as follows: for three objects

@@

Finally, the symmetric monoidal structure of $F\lCsp_1$ is inherited from that in $\A$ and $F$, with braiding $\beta\maps M_1\ot M_2\to M_2\ot M_1$ the cospan isomorphism

@@

>>>>

This can always be achieved by replacing $F$ by an equivalent pseudofunctor that strictly preserves identity morphisms \cite[Proposition 5.2]{LP}.  We do this merely to reduce the size of  our diagrams; the reader can reinsert the morphism $F(!_0)$ where needed. %%% see if you like this!  - jb 
The associator in is formed as follows: for three objects

@@

Finally, the braiding in $F\lCsp_1$ is inherited from that in $\A$ and $F$, with braiding $\beta\maps M_1\ot M_2\to M_2\ot M_1$ the cospan isomorphism

@@

\bibitem{LP} S.\ Lack and S.\ Paoli, 2-nerves for bicategories, \textsl{$K$-Theory} \textbf{38} (2008), 153--175.
